Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-13 paper.tex
done 3.6

\paragraph{Extensibility} Adding a new engine type requires to wrap
the engine in the agent and to update interactions \texttt{b} and
\texttt{c$_2$} (\texttt{E$_1$=3}). Updating the version of an engine
is transparent (\texttt{E$_2$=0}) since it only requires updating the
agent that is a component dedicated to the engine. Integrating a new workflow is
done through interactions \texttt{a$_1$} and \texttt{a$_2$}
(\texttt{E$_3$=2}). Integrating a new infrastructure requires updates
in interactions \texttt{a$_1$}, \texttt{b}, \texttt{c$_1$} and \texttt{c$_2$}
(\texttt{E$_4$=4}).

\paragraph{Scalability} New engine instances only require new agents,
which is easily automated (\texttt{S$_1$=0}) and by design very
suitable for elastic computing.\closednote{Naj}{I feel the concept of elastic computing should be mentioned in introductory sections}{Tristan}{You are right, this is now fixed.} For instance, auto-scaling rules can
be implemented to start new agents when the workload in the science
gateway exceeds a certain threshold~\cite{lorido2012auto}. Distributed
engines are not available by default (\texttt{S$_2$=1}) and task
scheduling is as complex as in any other architecture
(\texttt{S$_3$=0}).

\paragraph{Specific features} Meta-workflows are not available by default
(\texttt{O$_1$=1}).  Accessing debugging information is not likely to
be an issue since the workflow pool could implement specific functions
for that (\texttt{O$_2$=0}).

>>>>

\paragraph{Extensibility} Adding a new engine type requires wrapping
the engine into the agent and updating interactions \texttt{b} and
\texttt{c$_2$} (\texttt{E$_1$=3}). Updating the version of an engine
is transparent (\texttt{E$_2$=0}) since it only requires updating the
agent, which is a component dedicated to the engine. Integrating a new workflow is
done through interactions \texttt{a$_1$} and \texttt{a$_2$}
(\texttt{E$_3$=2}). Integrating a new infrastructure requires updates
in interactions \texttt{a$_1$}, \texttt{b}, \texttt{c$_1$} and \texttt{c$_2$}
(\texttt{E$_4$=4}).

\paragraph{Scalability} New engine instances only require new agents,
which can be easily automated (\texttt{S$_1$=0}) and by design very
suitable for elastic computing.\closednote{Naj}{I feel the concept of elastic computing should be mentioned in introductory sections}{Tristan}{You are right, this is now fixed.} For instance, auto-scaling rules can
be implemented to start new agents when the workload in the science
gateway exceeds a certain threshold~\cite{lorido2012auto}. Distributed
engines are not available by default (\texttt{S$_2$=1}) and task
scheduling is as complex as in any other architecture
(\texttt{S$_3$=0}).

\paragraph{Specific features} Meta-workflows are not available by default
(\texttt{O$_1$=1}).  
\note{sil}{see comment in section 3.1}
Accessing debugging information is not likely to
be an issue since the workflow pool could implement specific functions
for that (\texttt{O$_2$=0}).
\note{sil}{i think the case here is the same as for service. or actually i would give this one a worse score, because there is one additional component - the pool - to cross}
